---
title: "HW 1"
author: "jose ortega"
format: html
embed-resources: true
editor: visual
---

## 

## **Question 1:**

I installed the three packages. But I did it in the console as I was instructed to do.

## **Question 2:**

```         
```

```{r}
library(causact)
library(dplyr)
library(igraph)
```

```         
```

df \<- as_data_frame(x = c(1,2,3))

Says Error in \`ensure_igraph()\`:
! Must provide a graph object (provided wrong object type).
Backtrace:
 1. igraph::as_data_frame(x = c(1, 2, 3))
2. igraph:::ensure_igraph(x)

```{r}
df <- dplyr::as_data_frame(x = c(1,2,3))
```

```{r}
glimpse(df)
```

This worked because we specified it as dplyr.

```{r}
?n_distinct()
```

```{r}
x <- c(5,6,2,7,9,1)
n_distinct(x)
```

We had not specified dplyr and we were using igraph as it was the most recent version we downloaded.

## **Question 3**

```{r}
?n_distinct()
```

n_distinct basically says how many different sets of a single number there are. In question 2 with a total of 6 numbers, each number was presented only once so it was \[1\] with 6 numbers.

## **Question 4**

```{r}
glimpse(baseballData)
```

12,145 rows

5 columns

Home is a categorical variable and HomeScore is quantitative variable

## **Question 5**

```{r}
baseballData[1,]
```

One row corresponds to a specific observation. Here, the observation is a specific baseball game.

```{r}
baseballData[,2:3] %>% head()
```

These columns correspond to the variables which are related top the different observations.

## **Question 6**

```{r}
name <-
  c(
    "Wayne Gretzky",
    "Gordie Howe",
    "Jaromir Jagr",
    "Brett Hull",
    "Marcel Dionne",
    "Phil Esposito" ,
    "Mike Gartner",
    "Alex Ovechkin",
    "Mark Messier" ,
    "Steve Yzerman"
  )

goals <- c(894, 801, 766, 741, 731, 717, 708, 700, 694, 692)

year_started <- c(1979, 1946, 1990, 1986, 1971, 1963, 1979, 2005, 1979, 1983)
```

```{r}
dr <- tibble(
  goals=goals,
  year_started=year_started,
  name=name,
)
glimpse(df)
```

```{r}
## simplest version
```
