---
title: "DV 1-3"
author: "Jose Ortega"
format: html
embeded-resources: true
editor: visual
---

## HW 5

## Question 1

```{r}
library(tidyverse)
# Read in the data 
exercise_data <- read_csv("https://raw.githubusercontent.com/vaiseys/dav-course/main/Data/visualize_data.csv")
glimpse(exercise_data)
```

My guess is that people who exercise more will have a higher BMI.

```{r}
cor(exercise_data$Exercise, exercise_data$BMI)
```

The output indicates the correlation between exercise and BMI.

```{r}
ggplot(data = exercise_data, mapping = aes(x = Exercise, y = BMI)) + 
  geom_point()
```

## Question 2

```{r}
library(causact)
glimpse(corruptDF)
```

```{r}
?corruptDF
```

CPI2017 and HDI2017 describe the Corruption Index for countries across the world in 2017 and the Human Development Index for countries across the world in 2017.

## Question 3

```{r}
ggplot(data = corruptDF, mapping = aes(x = HDI2017, y = CPI2017)) + 
  geom_point()
```

CPI and HDI have a positive relationship where as one increases, the other increases as well over time.

## Question 4

```{r}
ggplot(data = corruptDF, mapping = aes(x = HDI2017, y = CPI2017)) + 
  geom_point() +
geom_smooth(method = "lm", se = FALSE)
```

The "regression line" suggests that there is a positive relationship between the two variables HDI and CPI of 2017. The more human development the more corruption over time.

## Question 5

```{r}
ggplot(data = corruptDF, mapping = aes(x = HDI2017, y = CPI2017)) + 
  geom_point() +
geom_smooth(method = "lm", se = FALSE)
```
