---
title: "HW 2"
author: "Jose Ortega"
format: html
embed-resources: true
editor: visual
---

## **HW2** 

```{r}
library(tidyverse)
```

```{r}
olympics  <- read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2021/2021-07-27/olympics.csv')
glimpse(olympics)

```

```{r}
glimpse(olympics)
```

```{r}
table(olympics$medal)
```

## **Question 1**

```{r}
library(tidyverse)

olympics  <- read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2021/2021-07-27/olympics.csv')
glimpse(olympics)

table(olympics$medal)



gold_medalists <- olympics %>%
  filter(medal == "Gold")
```

There are 13372 rows resulting from the data for gold medalists.

## Question 2

```{r}
ggplot(data = gold_medalists, 
       mapping= aes(x= year, y= age)) +

geom_point(alpha=0.2)
```

The most appropriate graph for this data is a scatter plot. The data hows that the athletes get younger as the years increase. **The solution to over plotting is changing the transparency/ opacity to see the data points more clearly and highlight the more valuable data through alpha.**

## **Question 3**

```{r}
us_medals <- gold_medalists %>% 
  filter(noc == "USA") %>% 
  group_by(year) %>% 
  summarise(num_medals = n())
```

```         

```

```{r}
ggplot(data= us_medals,
       mapping= aes(x=year, y= num_medals)) +
  geom_line()
```

The most successful year was around 1982-83. There are more squiggly lines towards the end of the graph because of the increase in competition as a guess.

## **Question 4**

```{r}
two_events <- gold_medalists %>%
  filter(
    event == "Gymnastics Men's Individual All-Around" | 
      event == "Gymnastics Women's Individual All-Around" |
      event == "Athletics Women's 100 metres"   |
      event == "Athletics Men's 100 metres"
  ) 
```

```{r}
gymnastics <- gold_medalists %>%
  filter(event == "Gymnastics Men's Individual All-Around" | 
      event == "Gymnastics Women's Individual All-Around")


```

This filters to just Gymnastics events.

```{r}
ggplot(data = gymnastics, mapping = aes(x = age)) +
  geom_histogram(color= "white")
```

This histogram shows the age of each athlete and how many athletes there are at the specific age.

```{r}
ggplot(data = gymnastics, mapping = aes(x = age)) +
  geom_histogram(color= "white") +
  facet_wrap (~event)

```

Based on the data, men seem to be older in this data for gymnastics.

## **Question 5**

```{r}
ggplot(data = two_events, mapping = aes(x = event, y= height)) +
  geom_boxplot() + theme(axis.text.x = element_text(angle = 20, size = 6))
  
```

The data shows that on average, male runners and male gymnasts are taller than the female runners and female gymnasts.

## **Question 6**

```{r}
us_medalists <- gold_medalists %>% 
  filter(noc == "USA")
```

```{r}
ggplot(data = us_medalists, mapping = aes(x = year, color= sex, group= sex, fill= sex)) +
  geom_bar(position= "dodge")
```

Over the years, the number of gold medals increased on average, with a bit of a decrease between years in the 2000s. The males substantially have gained more medals than the females, but the females have a greater increase from 1990-2000.
